Self-assembly of colloid-cholesteric composites provides a route to switchable optical materials

### 2014-02-20 trunk/papers/2012-sandwich/response.txt

Date: Mon, 17 Feb 2014 04:37:57 -0500
From: c.huang@nature.com
To: dmarendu@ph.ed.ac.uk
Subject: Decision on manuscript NCOMMS-14-00180-T

** Please ensure you delete the link to your author home page in this e-mail
if you wish to forward it to your coauthors **

Dear Dr Marenduzzo,

Your manuscript entitled "Self-assembly of colloid-cholesteric composites: A
route to switchable optical materials" has now been seen by 2 referees,
whose comments are appended below. You
will see that, while they find your work of interest, they have raised
points that need to be addressed before we can make a decision on
publication.

We therefore invite you to revise and resubmit your manuscript, taking into
account the points raised. At the same time, we ask that you ensure your
manuscript complies with our format
requirements, which are summarized in the following checklist:
http://www.nature.com/ncomms/authors/ncomms_manuscript_checklist.pdf

Please use the following link to submit your revised manuscript, completed
checklist and point-by-point response to the referees' comments (which
should be in a separate document to any
cover letter):
http://mts-ncomms.nature.com/cgi-bin/main.plex?el=A6S2Lka4A1DfBL5I4A9v6k5dsV
e8yORLGQzsElBAZ

** This url links to your confidential home page and associated information
about manuscripts you may have submitted or be reviewing for us. If you wish
to forward this email to co-authors,
please delete the link to your homepage first **

We hope to receive your revised paper within two months; please let us know
if you aren't able to submit it within this time so that we can discuss the
best way forward. If we don't hear
from you, and the revision process takes significantly longer, we will close
your file. In this event, we will still be happy to reconsider your paper at
a later date, as long as nothing
similar has been accepted for publication at Nature Communications or
published elsewhere in the meantime.

We look forward to hearing from you soon.

Best regards,

Congcong Huang, PhD

Associate Editor
Nature Communications

Unit 10-11, 42F, The Center
989 Changle Road, Xuhui District
Shanghai, China, 200031
Tel: +86-21-2422-5011
Fax: +86-21-2422-5015
www.nature.com/naturecommunications

Reviewers' comments:

Reviewer #1 (Remarks to the Author):

The authors describe the results of a study of colloidal particles dispersed
in cholesteric blue phases (BP) focusing on the effects of particle
concentration and distribution. Additionally
effects of confinement and external fields are investigated. The use of the
lattice Boltzmann approach allows to follow dynamics after the thermal
quench and electric field application. The
study is an important step in modeling of BPs and should deserve a
publication in Nature Communications. Nevertheless there are some weak
points that need improvement before the publication.
Below is the list of remarks.

General remarks:

The term colloid is by the definition a dispersion of particles in a fluid.
Using the term also for the particles my lead to a confusion. In the
manuscript often also a more appropriate word
colloidal particle is used.

It would be important to add comments that would help experimentalist in
designing experiments with colloidal blue phases and perhaps stimulate
development of applications on the base of
these materials.

Particular remarks:

Page 2

In the discussion of the physical understanding of trapping of colloidal
particles in BP disclination networks it would be useful to refer to the
initial study by Ravnik et al. in Faraday
Discussions 2009 devoted to this topic.

250 K is more than the total mesophase stability range!

Page 3

The statement "This is defined such that W > 0 gives preferential
perpendicular orientation of the director field at the particle surface." is
not consistent with the interaction form
described in the Supplement.

For potential readers it would be useful to specify the particle radius in
nanometers in the main text. How it compares to the nematic correlation
length? How the radius influences the
structures? How tiny the particles can still be that the method based on the
Landau-de Gennes free energy is justified.

Is WR/K = 2.8 justified for nanoparticles used in the study?

Page 4:

Can the G elastic modulus be estimated for modeled structures?

Page 5:

Can annealing of the structures obtained with the thermal quench lead to
ordered colloidal structures?

Is also in case of the disordered structures observed a change in the
stability range of the colloidal BPs?

In the discussion of colloidal particles in BP thin layers it would be good
to comment the study of
Ravnik et al. in Soft Matter 2011 devoted the ordered structures of such a
system.

Page 6:

It would be good to comment the difference between structures in the bulk
and thin layer for particles with strong anchoring. Does this depend on the
visualization or is more behind?

Are the electric field induced changes irreversible only in case of
colloidal dispersions?

Page 7

Reference 2 has a mistake.

Supplement

Segment 4.2:

The statement "Wall anchoring is either normal or planar with W=K = 1 in
simulation units" is unclear.

References of the Supplement:
There are mistakes in references 1 and 2.

Reviewer #2 (Remarks to the Author):

This paper, "Self-assembly of colloid-cholesteric composities: A route to
switchable optical materials" reports simulations of the formation of
particle networks in a cholesteric host and in
particular in the blue phase of the cholesteric host. It reports the
influence of various physical parameters and in particular the surface
anchoring and concentration of the colloidal
particles. The paper also reports how external fields can be employed to
change the morphology of these colloidal composites and how this may be
employed in practical optical devices.

The paper builds on a body of previous research, both theoretical and
experimental that has explored the effects of dispersing particles in a
liquid crystal host. The novelty of the paper is
to model the effect of particles in the blue phases of a cholesteric host
ahd to postulate how these colloids may be employed in specific
appilcations.

I am not a theorteical physiscist and therefore will not comment on the
methodology but rather will take the perspective of an experimentalist and
how useful this paper is in understanding
these materials and more importantly how useful the paper is in suggesting
and designing experimental procedures and developing the actual materials.

The paper provides insight into the effectiveness of including particles
into the blue phase as a means of controlling and adjusting the structure
and stability of the materials. The paper
is clearly written and the figures, paricularly the included 3D videos,
provide clear perspective on the modeled phases of these materials. The
results are of interest and useful to
experimentalists working in the field. The paper would be even more useful
if it included references to actual materials, both the liquid crystal host
and the added particles and perhaps
even suggested a model system that would be a good starting point to study
experimentally. In a similar vein, it would also be useful to address the
practical issue of reproducibility, which
has been a major problem with these materials. The theoretical results
clearly indicate how important the formation conditions are to the final
result. What is the authors sense of how easy
it will be to reproducibly fabricate a device
with a specific morphology and optical properties. This seems a likely
practical issue particularly with the rich variety of structures reported in
the simulations.

** See NPG's author and referees' website at www.nature.com/authors for
information about policies, services and author benefits

This email has been sent through the NPG Manuscript Tracking System
NY-610A-NPG&MTS

Confidentiality Statement:

This e-mail is confidential and subject to copyright. Any unauthorised use
or disclosure of its contents is prohibited. If you have received this email
in error please notify our Manuscript
Tracking System Helpdesk team at http://npgapps.custhelp.com/app/ask.

Details of the confidentiality and pre-publicity policy may be found here
http://www.nature.com/authors/policies/confidentiality.html

Privacy Policy | Update Profile

### 2014-02-21 papers/2012-sandwich/CholColloids.tex
First revision update
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@2312 40876441-3496-0410-a613-a2fca35b2ae2

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  Main text for ``sandwich'' manuscript
%
%  Process with ``pdflatex CholColloids.tex''
%
%  The supporting material text is support.tex
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\title{Self-assembly of colloid-cholesteric composites: A route to switchable optical materials}
\author{K. Stratford$^{*}$, O. Henrich$^{*}$, J.~S. Lintuvuori$^{*}$,\\
M. E. Cates, D. Marenduzzo \\ 
{\small SUPA, School of Physics and Astronomy, Edinburgh University,} \\
\small{Edinburgh, EJ9 3JZ, UK}\\
\small{$^{*}$ equally contributed to this work}}
\date{}

@@

{\bf Colloidal particles dispersed in liquid crystals can form new materials with tunable elastic and electro-optic properties~\cite{stark}. In a host comprising  a periodic `blue phase' chiral liquid crystal~\cite{mermin}, the particles should template into colloidal crystals \cite{miha} with potential uses in photonics, metamaterials, and transformational optics~\cite{lavrentovich}. 
Here we show by computer simulation that colloid/cholesteric mixtures can give rise to a much wider range of soft-solid composites than previously anticipated. These include regular crystals, glasses, percolating gels, isolated clusters, twisted rings and undulating colloidal ropes. The final structure can be tuned via the particle concentration, and by varying the surface interactions of the cholesteric host with both the colloids and any confining walls. 
Remarkably, we find that many of these new materials are metastable: two or more structures can arise under identical thermodynamic conditions. The observed structure depends not only on the formulation protocol,
but also on the history of an applied electric field.  
This new class of soft materials should thus be relevant to the design of switchable, multistable devices for optical technologies including, for example, smart glass and e-paper~\cite{epaper}.}

When spherical colloidal particles are mixed into a nematic liquid crystal, 
they disrupt the orientational order in the fluid and create defects (disclination lines) in the nematic close to their surfaces. To minimize the free energy cost, it is generally advantageous for defects to be shared:
therefore the colloidal particles have a generic tendency to aggregate. Such aggregates may further 
self-assemble into lines~\cite{wiresmiha}, 2D crystals~\cite{zumer}, 
planar structures~\cite{tanaka}, or 3D amorphous glasses~\cite{tiffany}.
Besides being of fundamental interest to materials science, these
structures may have tunable elastic and optical properties~\cite{stark}. Hence 
they offer exciting prospects for applications as biosensors~\cite{abbott}, or
as new devices~\cite{colloiddevice,tanakanatmat}.

But one may also choose to disperse colloidal particles in a cholesteric, 
rather than nematic, liquid crystal. The molecules making up this material are
chiral, and this causes their average orientation (described by a director field) to rotate in space in
a helical fashion, rather than remain uniform as in nematics. 
This typically creates a 1-dimensional periodic structure, called the cholesteric phase, whose wavelength 
is the pitch, $p$. The periodicity can however become fully three dimensional in the so-called blue phases (BPs)~\cite{mermin}. BPs arise because the director field can twist around more than one direction at once (see 
the cartoon in Fig. S1). Such double twist 
regions (generally cylinders: DTCs) are energetically favoured at high enough molecular chirality, but
lead to geometric frustration because it is impossible to tile the whole 3D
space with DTCs without also introducing ``disclination lines'' 
(These are singular topological defects on which the director field is 
undefined.) In blue phases these disclination lines themselves either form a 3D periodic regular lattice (in so called BPI and BPII), or remain disordered (BPIII)~\cite{bp3}. 
%
BPs are stabilised by the tendency of chiral molecules to twist, but destabilised by the cost of forming topological defects (which locally diminish the molecular alignment). In conventional cholesteric materials~\cite{mermin} this balance is only achievable in a narrow temperature range of a few degrees, around the onset of liquid crystalline ordering. However, recent advances in formulation have widened this stability range enormously (up to 250K) paving the way to
applications of BPs in display devices~\cite{kikuchi,bplasers,coleswidetrange,bpdevice,coles}.

Besides being remarkable materials in themselves, BPs offer significant promise as hosts for dispersing colloidal particles. Because BPs contain a disclination network even in the absence of
particles, they can potentially template colloidal self-assembly. 
This was proved recently by simulations of BP-dispersed nanoparticles which 
exclude the surrounding liquid crystal but otherwise have negligible surface 
interaction with it (to give a so-called `weak anchoring' regime)~\cite{miha}. 
Such particles are attracted to the disclination network in BPs: by covering up the defect cores, the high elastic energy cost of those regions is avoided. The pre-existing order of the defect network then templates particles into a regular colloidal crystal of the same periodicity. 
Because this structure has a wavelength in the visible range, 
the resulting material should inherit (and likely enhance) the incomplete photonic bandgap of the parent blue phase, as exploited for instance in laser devices~\cite{bplasers}; for related possibilities see \cite{lavrentovich}.

A second compelling reason to study colloid-BP composites is that, even without particles, BPs can show several competing metastable free energy minima,
corresponding to different topologies of the defect network~\cite{adriano,fukuda}, with a strong dependence on applied electric or magnetic fields~\cite{henrichfield}.
% 
Adding particles is likely to further enrich the free energy landscape, creating composites that might be promising candidates for bistable or multistable devices, in which energy is needed only to switch optical properties and not to maintain them. (This is the e-paper paradigm~\cite{epaper}, and can lead to huge energy savings.)
To explore such metastability, and switching strategies between states, we require multi-unit-cell, time-dependent simulations. These go beyond previous studies of colloid-BP composites~\cite{miha} but follow comparable simulations of pure BPs~\cite{bp3,henrichfield,domaingrowth}, and isolated and dimeric colloids in cholesterics~\cite{juho1,juho2}. Our methodology and simulation parameters are summarized in the Supplementary Information.

We show in Fig.~1 A-D the final state structures of four simulations in which we first equilibrated a stable BPI disclination network in bulk (with periodic boundary conditions) and then dispersed colloidal particles at random within it. Among dimensionless control parameters are the colloid volume fraction $\phi$  ($\phi = 1\%$ or $5\%$); the ratio $r = R/\lambda$ of particle radius to the BP lattice parameter $\lambda$ (here $r\simeq 0.14$) and the ratio $w = WR/K$ where $W$ is the anchoring strength of the cholesteric at the particle surface, and $K$ is the elastic constant of the liquid crystal. (This is defined such that $W>0$ gives preferential perpendicular orientation of the director field at the particle surface.) For the latter we choose $w = 0.23, 2.3$ which are within typical experimental range~\cite{tiffany}. This parameter can be viewed as the ratio of the anchoring energy, $WR^2$, to the elastic energy scale for distortion $KR$.

For a single colloidal particle in a nematic fluid, $w$ controls the formation of a local topological defect at the particle surface~\cite{stark}, with weak distortion of the nearby fluid at small $w$. In the colloid-BP system, $w$ also plays a determining role in the final composite structure. When $w$ is small (Fig.~ 1A,B; Suppl. Movie 1,2), the attraction of particles to the disclination lattice causes
 the lattice to become covered by particles, with little disruption of its
 long-range order. Thus a templated colloidal crystal is created, as first reported in~\cite{miha}. Interestingly, the weak but finite anchoring apparently creates an elastic force between the colloids which leads to very slow dynamics (Fig. S4) and the formation of small colloidal lines within disclinations, especially for dilute samples (Fig. 1A). It seems likely that polymer-stabilised  blue phases~\cite{kikuchi} work by a similar principle to this small $w$ case, with a weak segregation of monomers towards the defect regions.

For large $w$ (Fig.~1C,D; Suppl. Movie 3,4), the picture changes dramatically.
Each colloidal particle now disrupts significantly the order of the nearby fluid, with defect formation close to its surface~\cite{stark}. The resulting strong disruption of local liquid crystalline order around each particle leads now to 
a strong interparticle attraction. This restructures the disclination
network completely, destroying the long range order of
the original BPI topology. Most notably, particle aggregation favours
the formation of defect junctions, where four disclinations meet. This structural motif is present in the unit cell of BPII rather than BPI (and also seen in the amorphous BPIII~\cite{bp3}). The particle clusters are disjoint at low volume fractions ($\phi\simeq 1\%$) but they interact elastically via the connecting disclinations. At larger $\phi$, the aggregates join up to form a percolating colloidal cluster which essentially templates the disclinations rather than vice versa.

As colloid-nematic composites~\cite{tiffany}, all the structures in Fig.~1A-D 
should be soft solids, of nonzero elastic 
modulus $G$ at low frequency. This contrasts with pure BPs, where
$G=0$ as the fluid can flow with a finite
viscosity via permeation of molecules through a fixed defect lattice~\cite{permeation1,permeation2}. We expect the
structures in Fig.~1A-C to be only weak gels, as here the 
defect network percolates but particle contacts do not. This is broadly similar to the cholesteric-nanoparticle gel reported
in~\cite{lubensky} (with $G<1$ Pa). In contrast, the colloidal gel
structure in Fig.~1D should be much more resistant mechanically, 
due to the formation of a thick percolating particle network. The 
structure is now akin to that of the self-quenched glass found in 
colloid-nematic composites~\cite{tiffany} at much higher volume 
fraction (over 20\% as opposed to below 5\% here), for which $G\sim 10^3$ Pa.

A more practical protocol for including particles in a BPI phase is to disperse the particles at random in an isotropic phase, and then quenching this into the temperature range where BPI is stable. Here we know that, without particles, the kinetics can favour disordered (BPIII-like) intermediates which may be long lived or even metastable~\cite{domaingrowth}. Fig.~1E-H shows outcomes of such a quench protocol with the same parameter sets as in Fig.~1A-D. For small $w$, the particles again decorate the disclination lines, but are this time templated onto an amorphous network rather than an ordered one.
Increasing the volume fraction (Fig.~1F) leads to a more even coverage with
a better defined particle spacing. 
For large $w$, on the other hand, strong interparticle forces again dictate
the self-assembly. At low concentrations, discrete particle clusters decorate an amorphous defect lattice (Fig.~1G) whereas at higher $\phi$ a percolating network of colloid strands (the gel in Fig.~1H) is again seen. 
The structures in Fig. 1A-H have been followed for $\sim$20 ms 
(see Fig. S4); they correspond to either very slowly evolving states or 
deep metastable minima (elastic interactions are of
order $KR$ and dwarf thermal motion, see
Fig. S4 and Ref.~\cite{stark,lavrentovich}).

In display devices and other optical applications, it is typical for liquid crystals to be strongly confined (and subject to strong boundary effects), in contrast to the bulk geometries considered above. We therefore next describe how colloidal suspensions self assemble in thin sandwiches (thickness $h = 1.75 \lambda$), whose confining walls can favour either tangential (planar degenerate) or normal (homeotropic) orientation of the director field. For simplicity we here impose one or the other as a strict boundary condition.

Fig.~2A-D shows the case of normal wall anchoring on varying $\phi$ and $w$. We quench from the isotropic to the ordered phase as was done in Fig.~1E-H, and again find a metastable, amorphous disclination network (see Supplementary Information). The resulting colloid-cholesteric composites are somewhat similar to those seen in the bulk: for small $w$ the particles are templated by the network (Fig.~2A,B), whereas for large $w$ we observe isolated clusters (Fig.~2C) and percolated colloidal gels (Fig.~2D), for $\phi = 1\%$ and $4\%$ respectively. There are, however, significant effects of the confining walls.
First, the normal anchoring at the wall recruits particles there,  giving (for the chosen $h$) a density enhancement of the colloids at both walls 
(see side-views in Fig.~2A-D). Second, the clusters formed at large $w$ are themselves anisotropic with an oblate habit. These clusters
are similar to those reported experimentally for large colloids in a
cholesteric (but non-BP) host~\cite{niek}.

Fig.~2E-H shows comparable simulations for planar wall anchoring. 
Without colloids, planar anchoring results in a regular cholesteric helix,
with axis perpendicular to the boundary walls. 
This twisted texture develops via a set of defect loops,
which shrink and disappear to leave a defect-free sample. However,
dispersing particles with small $w$ arrests the loop shrinking process,
stabilising twisted rings (Fig.~2E) at small $\phi$, and more complicated 
double-stranded structures at larger $\phi$ (Fig.~2F).
For larger $w$, we observe thick colloidal ``ropes" about 5 colloids across
(Fig.~2G,H). These ropes undulate to follow the chiral structure of the 
underlying fluid. On increasing the density they develop branch points and finally again approach a percolating gel morphology. Note that planar wall anchoring is incompatible with the normal anchoring on the colloids (for $w>0$), which are thus repelled from both walls (see the side views in Fig.~2E-H).

An interesting question, relevant for applications to devices, is whether 
these structures can be modified, or switched, with electric fields.
Fig.~3 addresses this question, starting from amorphous Blue Phase III,
this time at a higher chirality. Dispersing colloids in this networks
results in the particle occupying the available nodes, where the order
parameter is low (Fig.~3A; Suppl. Movie 5). Applying a high enough field 
along the $x$ direction leads to a switching to a new phase, where colloidal 
arrays fit within a network with distorted hexagonal cells (Fig.~3B 
and Fig. S7; Suppl. Movie 6). 
Remarkably, upon field removal this honeycomb structure does not find its 
way back to the 
configuration before switching on the field, but gets stuck into a metastable 
structure (Fig. S7), with residual anisotropy along the field switching 
direction. Cycling the field along the $x$ and $y$ directions leads to
distinct metastable structures, which are retained after field removal
(Fig. S8 and S9).
%The resulting multistability is a prerequisite for new generation 
%switchable electrooptic devices for use in energy-saving electronics-free
%appliances, smart glass, and e-paper to cite just a few examples.

@@

\bibitem{stark} H. Stark. Physics of
colloidal dispersions in nematic liquid crystals. 
{\it Phys. Rep.} {\bf 351}, 387-474 (2001).
\bibitem{mermin} D.~C. Wright, Mermin, N.~D. Crystalline liquids: The blue phases. {\it Rev. Mod. Phys.} {\bf 61}, 385–432 (1989).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  Main text for ``sandwich'' manuscript
%
%  Process with ``pdflatex CholColloids.tex''
%
%  The supporting material text is support.tex
%
%  Submitted version was SVN 2259.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\title{Self-assembly of colloid-cholesteric composites provides
a route to switchable optical materials}

\author{K. Stratford$^{*}$, O. Henrich$^{*}$, J.~S. Lintuvuori$^{*}$,\\
M. E. Cates, D. Marenduzzo$^\dagger$ \\ 
SUPA, School of Physics and Astronomy, The King's Buildings,\\
The University of Edinburgh, Edinburgh, EJ9 3JZ, UK\\
\small{$^{*}$ equally contributed to this work}\\
\small{$^\dagger$ Corresponding author: dmarendu@ph.ed.ac.uk}
}
\date{}

@@

\noindent

%% ABSTRACT 150 WORDS MAX NO REFERENCES
\noindent
{\bf
Colloidal particles dispersed in liquid crystals can form new materials
with tunable elastic and electro-optic properties. In a periodic `blue
phase' host, particles should template into colloidal crystals with
potential uses in photonics, metamaterials, and transformational optics.
Here we show by computer simulation that colloid/cholesteric mixtures can
give rise to regular crystals, glasses, percolating gels, isolated clusters,
twisted rings and undulating colloidal ropes. This structure can be tuned
via particle concentration, and by varying the surface interactions of the
cholesteric host with both
the particles and confining walls. Many of these new materials are metastable:
two or more structures can arise under identical thermodynamic conditions.
The observed structure depends not only on the formulation protocol, but also
on the history of an applied electric field. This new class of soft materials
should thus be relevant to design of switchable, multistable devices for
optical technologies such as smart glass and e-paper.
}
%% EXACTLY 150

\bigskip
\noindent
%% [Introduction: Max 1000 words; we have about 650]

\noindent
When spherical colloidal particles are mixed into a nematic liquid crystal, 
they disrupt the orientational order in the fluid and create defects (disclination lines) in the nematic close to their surfaces. To minimize the free energy cost, it is generally advantageous for defects to be shared:
therefore the colloidal particles have a generic tendency to aggregate. Such aggregates may further 
self-assemble into lines~\cite{wiresmiha}, 2D crystals~\cite{zumer}, 
planar structures~\cite{tanaka}, or 3D amorphous glasses~\cite{tiffany}.
Besides being of fundamental interest to materials science, these
structures may have tunable elastic and optical properties~\cite{stark}. Hence 
they offer exciting prospects for applications as biosensors~\cite{abbott}, or
as new devices~\cite{colloiddevice,tanakanatmat}.

But one may also choose to disperse colloidal particles in a cholesteric, 
rather than nematic, liquid crystal. The molecules making up this material are
chiral, and this causes their average orientation (described by a director field) to rotate in space in
a helical fashion, rather than remain uniform as in nematics. 
This typically creates a 1-dimensional periodic structure, called the cholesteric phase, whose wavelength 
is the pitch, $p$. The periodicity can however become fully three dimensional in the so-called blue phases (BPs)~\cite{mermin}. BPs arise because the director field can twist around more than one direction at once (see 
the cartoon in Supplementary Fig.~1). Such double twist 
regions (generally cylinders) are energetically favoured at high enough molecular chirality, but
lead to geometric frustration because it is impossible to tile the whole 3D
space with double twist cylinders without also introducing ``disclination lines'' 
(These are singular topological defects on which the director field is 
undefined.) In blue phases these disclination lines themselves either form a 3D periodic regular lattice (in so called BPI and BPII), or remain disordered (BPIII)~\cite{bp3}. 
%
BPs are stabilised by the tendency of chiral molecules to twist, but destabilised by the cost of forming topological defects (which locally diminish the molecular alignment). In conventional cholesteric materials~\cite{mermin} this balance is only achievable in a narrow temperature range of a few degrees, around the onset of liquid crystalline ordering.
\textcolor{red}{
However, recent advances in formulation have widened this stability
range enormously~\cite{kikuchi,bplasers,coleswidetrange,bpdevice}. Most
recently, templated BPs with a stability range of -125
to~125$^\circ$C have been reported \cite{coles}, paving the way to
applications of BPs in operational display devices.}

Besides being remarkable materials in themselves, BPs offer significant promise as hosts for dispersing colloidal particles. Because BPs contain a disclination network even in the absence of
particles, they can potentially template colloidal self-assembly. 
This was proved recently by simulations of BP-dispersed nanoparticles which 
exclude the surrounding liquid crystal but otherwise have negligible surface 
interaction with it (to give a so-called `weak anchoring' regime)~\cite{extrareference1,miha}. 
Such particles are attracted to the disclination network in BPs: by covering up the defect cores, the high elastic energy cost of those regions is avoided. The pre-existing order of the defect network then templates particles into a regular colloidal crystal of the same periodicity. 
Because this structure has a wavelength in the visible range, 
the resulting material should inherit (and likely enhance) the incomplete photonic bandgap of the parent blue phase, as exploited for instance in laser devices~\cite{bplasers}; for related possibilities see \cite{lavrentovich}.

A second compelling reason to study colloidal-BP composites is that, even without particles, BPs can show several competing metastable free energy minima,
corresponding to different topologies of the defect network~\cite{adriano,fukuda}, with a strong dependence on applied electric or magnetic fields~\cite{henrichfield}.
% 
Adding particles is likely to further enrich the free energy landscape, creating composites that might be promising candidates for bistable or multistable devices, in which energy is needed only to switch optical properties and not to maintain them. (This is the e-paper paradigm~\cite{epaper}, and can lead to huge energy savings.)
To explore such metastability, and switching strategies between states, we require multi-unit-cell, time-dependent simulations. These go beyond previous studies of colloidal-BP composites~\cite{miha} but follow comparable simulations of pure BPs~\cite{bp3,henrichfield,domaingrowth}, and isolated and dimeric colloidal particles in cholesterics~\cite{juho1,juho2}. Our methodology and simulation parameters are summarized in the Supplementary Information.

SHORT SUMMARY OF RESULTS AND CONCLUSIONS (PRESENT TENSE). To include a
statement about confined systems with reference to \cite{extrareference2}.
The simulations represent a liquid crystal
blue phase with unit cell size in the range of 100--500~nm \cite{mermin},
and particles with a radius of around 50~nm.

\bigskip
\noindent
\textbf{\large Results} [Currently about 1400 words]

\noindent
\textbf{Structure in bulk BPI.}
We show in Fig.~1 A-D the final state structures of four simulations in which we first equilibrated a stable BPI disclination network in bulk (with periodic boundary conditions) and then dispersed colloidal particles at random within it. Among dimensionless control parameters are the particle solid volume fraction $\phi$  ($\phi = 1\%$ or $5\%$); the ratio $r = R/\lambda$ of particle radius to the BP lattice parameter $\lambda$ (here $r\simeq 0.14$) and the ratio $w = WR/K$ where $W$ is the anchoring strength of the cholesteric at the particle surface, and $K$ is the elastic constant of the liquid crystal.
\textcolor{red}{
The anchoring strength is defined such that $W > 0$ imparts a preferred
orientation to the director field at the particle surface. This orientation
can be either normal to the surface or in a plane tengential to the surface,
a property related to surface chemistry in experimental systems but which
can be imposed at will in simulations.
We choose} $w = 0.23, 2.3$ which are within typical experimental range~\cite{tiffany}. This parameter can be viewed as the ratio of the anchoring energy, $WR^2$, to the elastic energy scale for distortion $KR$.

For a single colloidal particle in a nematic fluid, $w$ controls the formation of a local topological defect at the particle surface~\cite{stark}, with weak distortion of the nearby fluid at small $w$. In the colloidal-BP system, $w$ also plays a determining role in the final composite structure. When $w$ is small (Fig.~ 1A,B; Supplementary Movies~1 and~2), the attraction of particles to the disclination lattice causes
 the lattice to become covered by particles, with little disruption of its
 long-range order. Thus a templated colloidal crystal is created, as first reported in~\cite{miha}. Interestingly, the weak but finite anchoring apparently creates an elastic force between the colloidal particles which leads to very slow dynamics
(Supplementary Fig.~4) and the formation of small colloidal lines within disclinations, especially for dilute samples (Fig. 1A). It seems likely that polymer-stabilised  blue phases~\cite{kikuchi} work by a similar principle to this small $w$ case, with a weak segregation of monomers towards the defect regions.

For large $w$ (Fig.~1C,D; Supplementary Movies~3 and~4), the picture changes
dramatically.
Each colloidal particle now disrupts significantly the order of the nearby fluid, with defect formation close to its surface~\cite{stark}. The resulting strong disruption of local liquid crystalline order around each particle leads now to 
a strong interparticle attraction. This restructures the disclination
network completely, destroying the long range order of
the original BPI topology. Most notably, particle aggregation favours
the formation of defect junctions, where four disclinations meet. This structural motif is present in the unit cell of BPII rather than BPI (and also seen in the amorphous BPIII~\cite{bp3}). The particle clusters are disjoint at low volume fractions ($\phi\simeq 1\%$) but they interact elastically via the connecting disclinations. At larger $\phi$, the aggregates join up to form a percolating colloidal cluster which essentially templates the disclinations rather than vice versa.

As colloidal-nematic composites~\cite{tiffany}, all the structures in
Fig.~1A-D 
should be soft solids, of nonzero elastic 
modulus $G$ at low frequency. This contrasts with pure BPs, where
$G=0$ as the fluid can flow with a finite
viscosity via permeation of molecules through a fixed defect lattice~\cite{permeation1,permeation2}. We expect the
structures in Fig.~1A-C to be only weak gels, as here the 
defect network percolates but particle contacts do not. This is broadly similar to the cholesteric-nanoparticle gel reported
in~\cite{lubensky} (with $G<1$ Pa). In contrast, the colloidal gel
structure in Fig.~1D should be much more resistant mechanically, 
due to the formation of a thick percolating particle network. The 
structure is now akin to that of the self-quenched glass found in 
colloidal-nematic composites~\cite{tiffany} at much higher volume 
fraction (over 20\% as opposed to below 5\% here), for which $G\sim 10^3$ Pa.

A more practical protocol for including particles in a BPI phase is to disperse the particles at random in an isotropic phase, and then quenching this into the temperature range where BPI is stable. Here we know that, without particles, the kinetics can favour disordered (BPIII-like) intermediates which may be long lived or even metastable~\cite{domaingrowth}. Fig.~1E-H shows outcomes of such a quench protocol with the same parameter sets as in Fig.~1A-D. For small $w$, the particles again decorate the disclination lines, but are this time templated onto an amorphous network rather than an ordered one.
Increasing the volume fraction (Fig.~1F) leads to a more even coverage with
a better defined particle spacing. 
For large $w$, on the other hand, strong interparticle forces again dictate
the self-assembly. At low concentrations, discrete particle clusters decorate an amorphous defect lattice (Fig.~1G) whereas at higher $\phi$ a percolating network of colloidal strands (the gel in Fig.~1H) is again seen. 
The structures in Fig. 1A-H have been followed for $\sim$20 ms 
(see Supplementary Fig.~4); they correspond to either very slowly evolving
states or  deep metastable minima (elastic interactions are of
order $KR$ and dwarf thermal motion, see
Supplementary Fig.~4 and Ref.~\cite{stark,lavrentovich}).

\medskip
\noindent
\textbf{Structures in confined BPI.}
In display devices and other optical applications, it is typical for liquid crystals to be strongly confined (and subject to strong boundary effects), in contrast to the bulk geometries considered above. We therefore next describe how colloidal suspensions self assemble in thin sandwiches (thickness $h = 1.75 \lambda$), whose confining walls can favour either tangential (planar degenerate) or normal (homeotropic) orientation of the director field. For simplicity we here impose one or the other as a strict boundary condition.

Fig.~2A-D shows the case of normal wall anchoring on varying $\phi$ and $w$. We quench from the isotropic to the ordered phase as was done in Fig.~1E-H, and again find a metastable, amorphous disclination network (see Supplementary Information). The resulting colloidal-cholesteric composites are somewhat similar to those seen in the bulk: for small $w$ the particles are templated by the network (Fig.~2A,B), whereas for large $w$ we observe isolated clusters (Fig.~2C) and percolated colloidal gels (Fig.~2D), for $\phi = 1\%$ and $4\%$ respectively. There are, however, significant effects of the confining walls.
First, the normal anchoring at the wall recruits particles there,  giving (for the chosen $h$) a density enhancement of the colloid particless at both walls 
(see side-views in Fig.~2A-D). Second, the clusters formed at large $w$ are themselves anisotropic with an oblate habit. These clusters
are similar to those reported experimentally for large colloid particles in a
cholesteric (but non-BP) host~\cite{niek}.

Fig.~2E-H shows comparable simulations for planar wall anchoring. 
Without colloidal particles, planar anchoring results in a regular
cholesteric helix,
with axis perpendicular to the boundary walls. 
This twisted texture develops via a set of defect loops,
which shrink and disappear to leave a defect-free sample. However,
dispersing particles with small $w$ arrests the loop shrinking process,
stabilising twisted rings (Fig.~2E) at small $\phi$, and more complicated 
double-stranded structures at larger $\phi$ (Fig.~2F).
For larger $w$, we observe thick colloidal ``ropes" about 5 particles across
(Fig.~2G,H). These ropes undulate to follow the chiral structure of the 
underlying fluid. On increasing the density they develop branch points and finally again approach a percolating gel morphology. Note that planar wall anchoring is incompatible with the normal anchoring on the colloidal particles (for $w>0$), which are thus repelled from both walls (see the side views in Fig.~2E-H).

\medskip
\noindent
\textbf{Switching in electric field.}
An interesting question, relevant for applications to devices, is whether 
these structures can be modified, or switched, with electric fields.
Fig.~3 addresses this question, starting from amorphous Blue Phase III,
this time at a higher chirality. Dispersing colloidal particles in this networks
results in the particle occupying the available nodes, where the order
parameter is low (Fig.~3A; Supplementary Movie~5). Applying a high enough
field 
along the $x$ direction leads to a switching to a new phase, where colloidal 
arrays fit within a network with distorted hexagonal cells (Fig.~3B 
and Supplementary Fig.~7; Supplementary Movie~6). 
Remarkably, upon field removal this honeycomb structure does not find its 
way back to the 
configuration before switching on the field, but gets stuck into a metastable 
structure (Supplementary Fig.~7), with residual anisotropy along the field
switching 
direction. Cycling the field along the $x$ and $y$ directions leads to
distinct metastable structures, which are retained after field removal
(Suplementary Fig.~8 and Fig.~9).

@@

\bibitem{wiresmiha} M. Ravnik, M. Skarabot, S. Zumer, U. Tkalec, I. Poberaj,
D. Babic, N. Osterman, I. Musevic,
Entangled nematic colloidal dimers and wires, 
{\it Phys. Rev. Lett.} {\bf 99}, 247801 (2007).
